Robots, Are They Overlords or Serf-Laborers?

### 2015-06-11 draft1.tex
Add Lin et al to bibliography.
Replace hidden parts to the end to have a better overall look

% plagiarism check
% cohesion check
% grammar check (firt two page of new paper)
\documentclass[man]{apa6}
\title{Robots, Are They Overlords or Serf-Laborers?}
\author{Murat Ambarkutuk}
\affiliation{English Language Institute, University of Delaware \\ murata@udel.edu}
\note{First Draft; 6/8/2015; \LaTeX}
\usepackage{apacite}
% modify it!
\abstract{Of all the tools and methods invented by humankind to tame nature and make use of its challenges, the invention of computer has had the greatest impact on society. Coupled with the Internet, computers have changed the way billions of humans work, entertain themselves, and think. Since the rise of the computers, Artificial Intelligence (AI) has been one of the most debated issues in the field of engineering. Research toward the creation of AI includes a creation of self-aware machines that have superior intellectual abilities to that of human abilities. However, many researchers argue that the creation of AI will deeply change the society and it will help humankind to solve major societal problems, while others refute the arguments for the conceptual invention because of ethical problems that AI will bring such as an anticipated human annihilation by these agents. This paper focuses on the the ethical problems that the creation of AI will raise.} 
\keywords{artificial intelligence, robotics, ethics, society} 
\shorttitle{Overlords vs. Serf-Laborers}
\leftheader{Even-Numbered Page Header} %Change it
\begin{document}
\maketitle
% Citing examples \citeA{bost} \citeA{bry} \citeA{bob} \citeA{gre} \citeA{rosa} \citeA{duff}
\section{Introduction}
Even though the term robot was coined two centuries ago and the idea of AI emerged decades ago, some of the problems that have been raised by these two terms are yet to be solved. Sometimes, solutions for any arbitrary problem can be solved by seeing the bigger picture rather than scrutinizing tiny details. Thus, this paper focuses on numerous definitions for these terms and various applications of them which create intricacies and challenges in many level, varying from individual to societal level. Formation of this paper is as it follows: \#\#, \#\#, \#\#
%\section{A Brief History of Artificial Intelligence}
%The preliminary work that makes AI possible dates back to the first attempts to create computers; however, these research studies were limited in theoretical knowledge until the more sophisticated hardware was developed. For instance, the invention of faster Central Processor Units led researchers to have more calculation power and create more detailed and elaborate algorithms \cite{bost} Alan Turing, who is regarded the one who sets the basis for AI, created a test to question a machine's ability in its intelligence \cite{gre}. The second milestone of AI is invention of a programming language, Lisp (list processing), in the laboratories of Massachusetts Institute of Technology. Even though the concepts of AI existed before Lisp, it enabled researchers to use symbolic objects rather than numbers which was a major obstacle of AI creation. The other issue precluding the creation of AI is the challenges of information collection. As mentioned above, emulation of human cognitive and perceptual process have been a major method to implement AI. For that reason, natural language comprehension and visual information recognition have become two main focuses in AI research. Another example of the imitation of humanistic features is the structure of the human brain. The emergence of brand new sophisticated algorithms, namely, artificial neural networks and deep learning, also show significant resemblance to neural structure of the human brain which has enabled researchers to achieve more in the creation of AI.

@@

%\citeA{bry} claims that the common societal problems, such as the inequitable income distribution and poverty resulting from overpopulation, are impossible to cope with using regular tools and paradigms which governments now have. Having been scrutinizing social sciences, namely, developmental psychology and sociology, researchers might expand their interpretation of human behaviors which might enable them find new solutions for the given problems. Moreover, elimination of aging and eradication of diseases might be the possible consequence of the creation of AI \citeA{bost}. Both authors discuss AI's advanced reasoning and interpretation underlining the new opportunities that AI might bring to societies in order to solve chronic societal problems.

@@

\section{The Bigger Picture}
\subsection{What is a Robot?}
One common definition of AI is cited by \citeA{bost}, "A super-intelligence is any intellect that is vastly outperforms the best human brains in practically every field, including scientific creativity, general wisdom and social skills." This definition clearly distinguishes specific domain intelligent agents and AI. Based on this definition a computer system, Deep Blue, which is a well-known computer system for its success in chess can be considered smart within a narrow domain rather than a genuine AI supported by limitations that \citeauthor{duff} \citeyear[p.~34]{duff} speculates.\par

By literary definition the term robot is derived from the Czech word "roboti" meaning serf-labor. However, this definition closely refering to slave-like labourer has altered to something brand new as technology advances. In his article entitled "The Sheer Difficulty of Defining What a Robot Is", \citeA{pear} discusses two distinctive definitions of robotics that are posed by the prominent experts in the field of robotics. These two definitions emphasize different aspect of robotics creating important distinctions among them. The first definition puts emphasis on the successful combination of a rigid body responsible for interacting with its environment and a central reasoning unit responsible for reasoning tasks based perception and cognition. Without s software and hardware collaboration, as \citeA{pear} cited in his article, accomplishing its tasks for a robot cannot be possible.
The second definition, however, takes autonomy into account. A robot, \citeA{pear} quoted in his article, must have an detailed idea of any action formed by a tedious plan, accurate reasoning and precise action to interact with its physical environment. In light of these definitions, robots have to interact with its environment, which exclude any means of social interactions. However, \citeA{lan} asserts that socially interaction robots are significantly popular among society. Albeit popular, social robots, for instance a teacher robot or a guidance robot employed in an art gallery, seem to be decontextualized. This discrepancy brings about a major problem in individual and societal level. For instance, individuals have started to get strong advices from AI applications rather than a close friend who know better about the individual seeking advices, the taste of of music or book for instance, than a software crunching numbers faster than a man. Even though this issue seems to have a minor flipside, once it is aggregated, it will create true alienation from society and confussion regarding personhood, \citeA{lan} claims.\par
\subsection{What (should) does a Robot do?}
% A strip from the old paper
In order to make clear its obfuscated definition, the tasks of AI should be addressed. The task of AI is to create methods to enable machines to obtain symbolic data sets and manipulate them in order to solve generic problems in the most energy efficient and fastest fashion. The theory suggests that it is possible to achieve by imitating the processes of logical reasoning and decision making. Consequently, cognitive and perceptual systems of the human body have been scrutinized by researchers in order to emulate these processes at the hardware and software level.\par
Along with the definitions of robotics, the applications of it extensively vary which makes it hard to define or understand the task and the responsibilities of robots. \citeA{lan} gives different examples from a software tailored for "Jeopardy" to a teacher robot.
Although \citeA{pear} excludes any means of social interaction in the definitions of robotics proposed in this article, \citeA{rodhan} exemplifies an emerging application of robotics, a molecular level robot which identifies cancerous cells and attach them by releasing antibodies, thereby eliminating cancerous cells. Even though, experts have not been able to solve dilemma within the field of robotics, this case of sophistication within robotics exemplifies another complex issue.
The reason why these social interaction dilemma matter, whether in bodily level or molecular level, is that technology advances in faster pace that of the wisdom regarding robots and ourselves.\par

\section{Conclusion}
The notion of increasingly accelerating technology with the precious help of scientific research studies thrills individuals, and gives hope to patients.
%However, these two prominent terms of technology closely resembles another, the Internet.
%, otherwise yet another issue will jump into debate topics before formers could be solved. 
Yet, it is crucially important to decide whether or not robots are simply functional machines that are utilitarian in their responsibilities and nothing more. If so, it is irrelevant to discuss the ethical problems arisen by its creation because the problems will become a question of accuracy of the source code that runs robots and forms AI. In that case, the matter should be discussed would be how to prepare individuals, societies and governments its coming. As for the ethical problems, they will highly likely to be no more prone to erroneousness than any other human invention. If evolutionary and development psychology is taken into account, the first members of fully autonomous social robots will also evolve rapidly to their excellence. As the expansion and the accessibility to AI and robotics increase, the prediction of the aftermath has become decrepit due to the late response of individuals and their wisdom toward these technologies. Thus, robotics and AI should be scrutinized to understand and formulate its definitions and functions, otherwise yet another issue will jump into debate topics before formers could be solved. 
\bibliographystyle{apacite}
\bibliography{bibliography}
\end{document}

>>>>

% plagiarism check
% cohesion check
% grammar check (firt two page of new paper)
\documentclass[man]{apa6}
\title{Robots, Are They Overlords or Serf-Laborers?}
\author{Murat Ambarkutuk}
\affiliation{English Language Institute, University of Delaware \\ murata@udel.edu}
\note{First Draft; 6/8/2015; \LaTeX}
\usepackage{apacite}
% modify it!
\abstract{Of all the tools and methods invented by humankind to tame nature and make use of its challenges, the invention of computer has had the greatest impact on society. Coupled with the Internet, computers have changed the way billions of humans work, entertain themselves, and think. Since the rise of the computers, Artificial Intelligence (AI) has been one of the most debated issues in the field of engineering. Research toward the creation of AI includes a creation of self-aware machines that have superior intellectual abilities to that of human abilities. However, many researchers argue that the creation of AI will deeply change the society and it will help humankind to solve major societal problems, while others refute the arguments for the conceptual invention because of ethical problems that AI will bring such as an anticipated human annihilation by these agents. This paper focuses on the the ethical problems that the creation of AI will raise.} 
\keywords{artificial intelligence, robotics, ethics, society} 
\shorttitle{Overlords vs. Serf-Laborers}
\leftheader{Even-Numbered Page Header} %Change it
\begin{document}
\maketitle
% Citing examples and the author lists
% \citeA{bost} \citeA{bry} \citeA{bob} \citeA{gre} \citeA{rosa} \citeA{duff} \citeA{lin}
\section{Introduction}
Even though the term robot was coined two centuries ago and the idea of AI emerged decades ago, some of the problems that have been raised by these two terms are yet to be solved. Sometimes, solutions for any arbitrary problem can be solved by seeing the bigger picture rather than scrutinizing tiny details. Thus, this paper focuses on numerous definitions for these terms and various applications of them which create intricacies and challenges in many level, varying from individual to societal level. Formation of this paper is as it follows: \#\#, \#\#, \#\#

\section{The Bigger Picture}
\subsection{What is a Robot?}
One common definition of AI is cited by \citeA{bost}, "A super-intelligence is any intellect that is vastly outperforms the best human brains in practically every field, including scientific creativity, general wisdom and social skills." This definition clearly distinguishes specific domain intelligent agents and AI. Based on this definition a computer system, Deep Blue, which is a well-known computer system for its success in chess can be considered smart within a narrow domain rather than a genuine AI supported by limitations that \citeauthor{duff} \citeyear[p.~34]{duff} speculates.\par

By literary definition the term robot is derived from the Czech word "roboti" meaning serf-labor. However, this definition closely refering to slave-like labourer has altered to something brand new as technology advances. In his article entitled "The Sheer Difficulty of Defining What a Robot Is", \citeA{pear} discusses two distinctive definitions of robotics that are posed by the prominent experts in the field of robotics. These two definitions emphasize different aspect of robotics creating important distinctions among them. The first definition puts emphasis on the successful combination of a rigid body responsible for interacting with its environment and a central reasoning unit responsible for reasoning tasks based perception and cognition. Without a software and hardware collaboration, as \citeA{pear} cited in his article, accomplishing its tasks for a robot cannot be possible.
The second definition, however, takes autonomy into account. A robot, \citeA{pear} quoted in his article, must have an detailed idea of any action formed by a tedious plan, accurate reasoning and precise action to interact with its physical environment. In light of these definitions, robots have to interact with its environment, which exclude any means of social interactions. However, \citeA{lan} asserts that socially interaction robots are significantly popular among society. Albeit popular, social robots, for instance a teacher robot or a guidance robot employed in an art gallery, seem to be decontextualized. This discrepancy brings about a major problem in individual and societal level. One example of this fact is that individuals have started to get strong advice from AI applications, a software crunching numbers faster than a man can do, rather than a close friend who might know better about the individual seeking advice, such as the taste in music or book. Even though this issue seems to have a minor flipside, once it is aggregated \citeA{lan} claims, it will create true alienation from society and confusion regarding personhood. In other words, roboticists have not been able  to reach a consensus on the definition of robots the embodiment of AI, \citeA{lin} noted.\par
\subsection{What (should) does a Robot do?}
% A strip from the old paper
In order to make clear its obfuscated definition, the tasks of AI should be addressed. The task of AI is to create methods to enable machines to obtain symbolic data sets and manipulate them in order to solve generic problems in the most energy efficient and fastest fashion. The theory suggests that it is possible to achieve by imitating the processes of logical reasoning and decision making. Consequently, cognitive and perceptual systems of the human body have been scrutinized by researchers in order to emulate these processes at the hardware and software level.\par
Along with the definitions of robotics, the applications of it extensively vary which makes it hard to define or understand the task and the responsibilities of robots. \citeA{lan} and \citeA{lin} listed many different applications of robotics, from labourer robots to medical purpose robots and to personal care and companion robots.
Although \citeA{pear} excludes any means of social interaction in the definitions of robotics proposed in this article, \citeA{rodhan} exemplifies an emerging application of robotics, a molecular level robot which identifies cancerous cells and attack them by releasing antibodies, thereby eliminating cancerous cells. Even though, experts have not been able to solve dilemmas within the field of robotics, this steadily growing sophistication within robotics add more complex issues to the pile.
% The reason why these social interaction dilemma matter, whether in bodily level or molecular level, is that technology advances in faster pace than that of the wisdom regarding robots and ourselves.\par

\section{Conclusion}
The notion of increasingly accelerating technology with the precious help of scientific research studies thrills individuals, and gives hope to patients.
%However, these two prominent terms of technology closely resembles another, the Internet.
%, otherwise yet another issue will jump into debate topics before formers could be solved. 
Yet, it is crucially important to decide whether or not robots are simply functional machines that are utilitarian in their responsibilities and nothing more. If so, it is irrelevant to discuss the ethical problems arisen by its creation because the problems will become a question of accuracy of the source code that runs robots and forms AI. In that case, the matter should be discussed would be how to prepare individuals, societies and governments its coming. As for the ethical problems, they will highly likely to be no more prone to erroneousness than any other human invention. If evolutionary and development psychology is taken into account, the first members of fully autonomous social robots will also evolve rapidly to their excellence. As the expansion and the accessibility to AI and robotics increase, the prediction of the aftermath has become decrepit due to the late response of individuals and their wisdom toward these technologies. Thus, robotics and AI should be scrutinized to understand and formulate its definitions and functions, otherwise yet another issue will jump into debate topics before formers could be solved. 
\bibliographystyle{apacite}
\bibliography{bibliography}
\end{document}

@@

%\citeA{bry} claims that the common societal problems, such as the inequity of income distribution and poverty resulting from overpopulation, are impossible to cope with using regular tools and frameworks which governments now have. Having been scrutinizing social sciences, namely, developmental psychology and sociology, researchers might expand their interpretation of human behaviors which might enable them find new solutions for the given problems. Moreover, elimination of aging and eradication of diseases might be the possible consequence of the creation of AI \citeA{bost}. Both authors discuss AI's advanced reasoning and interpretation underlining the new opportunities that AI might bring to societies in order to solve chronic societal problems.

@@
